Streaming $2$-Center with Outliers in High Dimension

### 2015-04-14 paper.tex
Add Conclusion section

%----------------------- Title -----------------------------------------
\title{Streaming $2$-Center with Outliers in High Dimension}
\author{Hamid~Zarrabi-Zadeh\thanks{Department of Computer Engineering, 
	Sharif University of Technology. 
	{\tt zarrabi@sharif.edu}}
	\and 
}

@@

@@

>>>>

%----------------------- Title -----------------------------------------
\title{Streaming $2$-Center with Outliers in High Dimension}
\author{Hamid~Zarrabi-Zadeh\thanks{De`partment of Computer Engineering, 
	Sharif University of Technology. 
	{\tt zarrabi@sharif.edu}}
	\and 
}

@@

The problem without outliers (i.e., $z=0$) in general (Euclidean) space can not be approximated with a smaller than factor $2$ ($1.822$) unless $\mathbf{P}=\mathbf{NP}$ \cite{bern1996approximation}.
Gonzalez showed a $2$-approximation algorithm for this problem \cite{gonzalez1985clustering}.
For small $k$ and $d$, there are more efficient algorithms.
For Euclidean $1$-center in fixed dimensions, Chazelle~\etal gave a linear algorithm \cite{chazelle1996linear}.
For $2$-center in the plane the best known algorithm, runs in $\cO(n \log^2 n \log^2 \log n)$ and linear space, given by Chan \cite{chan1999more}.

In streaming data model, Guha \cite{guha2009tight}, in parallel with McCutchen~\etal \cite{mccutchen2008streaming} gave $(2+\eps)$-approximation for $k$-center without outliers.
For small $k$, better algorithms are known. For fixed $d$, there exists an $\eps$-coreset for $1$-center with $\cO(1 / \eps^{\frac{d-1}{2}})$ space.
For higher dimensions, Agarwal gave a $(\frac{1+\sqrt{3}}{2})$-approximation for $1$-center problem, and Chan \cite{chan2004faster} reduced its approximation factor to $1.22$, by an improved analysis.
For $k=2$, Ahn~\etal ~\cite{ahn2014computing} gave a $(2+\eps)$-approximation algorithm using $\cO(\frac{d}{\eps})$ space, which was improved for Euclidean spaces by Kim ~\etal \cite{kim2014improved} to a $(1.8+\eps)$-approximation algorithm, using the same space.

For the problem of $k$-center with outliers, Charikar ~\etal \cite{charikar2001algorithms} gives the first offline algorithm with approximation factor $3$ ($4$), where the candidate center points of the centers can be enumerated (otherwise).
For small $k$, there are better results known. $1$-center with $z$ outliers can be solved in $\cO(n \log z + z^{3} n^{\eps})$, for any $\eps > 0$, using Matou{\v{s}}ek's framework \cite{matouvsek1995geometric}.
Agarwal \cite{agarwal2008efficient} gives an algorithm with running time $\cO(n z^{7} \log^3 z)$ for $2$-center problem in $\IR^2$.

For the problem of $k$-center with $z$ outliers in streaming data model, McCutchen ~\etal \cite{mccutchen2008streaming} (using idea in Charikar ~\etal \cite{charikar2001algorithms} as subroutine) give a $(3+\eps)$-approximation ($(4+\eps)$-approximation, depending on the used subroutine) algorithm using $\cO(\frac{zk}{\eps})$ space.
In special case of $k=1$ in fixed dimensions, there exists a streaming algorithm with $\cO(\frac{z}{\eps^{\cO(d)}})$ space \cite{agarwal2007space, zarrabi2011almost}.
For Euclidean spaces, Zarrabi-Zadeh \cite{zarrabi2009streaming} gave $(1.22 \sqrt{2})$\nobreakdash-approximation for $1$-center with $z$ outliers running in $\cO(?)$ space.

In this paper we first give a simple $2$-approximation algorithm for $1$-center problem with space complexity $\cO(z^2 + zd)$. We then show a $(1.8 + \eps)$-approximation streaming algorithm for $2$-center with $z$ outliers in Euclidean space, with space complexity polynomial in $z$ and $d$ and sub-linear in $n$.

@@

%---------------------------- Conclusions ---------------------

\section{Conclusions}
\label{sec:conc}

In this paper, we presented an $(1.8 + \eps)$-approximation straming algorithm for $2$-center with $z$-outlier in euclidean space, which improves previous $3+\eps$-approximation algorithm by Charikar~\etal ~\cite{mccutchen2008streaming}. It remains open whether there can be any improvements in algorithm approximation factor. It is intresting problem to find an algorithm with better approximation factor and/or space complexity. It is also intresting to see if this algorithm can be generalized to a $k$-center with outliers in streaming data model with the same approximation factor (even for small $k$).
